Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
finished changes to the PE section

\begin{table}[t]
\begin{tabular}{c | c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
\hline
EdGB        & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
dCS         & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}  \\
cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.
}
\label{tab:ref_theories_qnms}
\end{table}

>>>>

\begin{table}[t]
\begin{tabular}{c | c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
\hline
EdGB        & 4 & 0.0107    & 0.0044    & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
dCS         & 4 & 3.1964    & 6.3619    & 41.199    & 794.66   &  \cite{Wagle:2021tam}  \\
cubic EFT   & 4 & $-$0.5813 & 2.6469    & $-$3.8620 & 265.12   & \cite{Cano:2021myl} \\
quartic EFT & 6 & $-$0.2114 & $-$0.6070 & $-$1.5263 & 171.35   & \cite{Cano:2021myl}  \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.
}
\label{tab:ref_theories_qnms}
\end{table}
